%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% One Page Two Column Resume
% LaTeX Template
% Version 1.4 (17/12/2023)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% v1.3 author:
% Zachary Taylor
%
% v1.3 repository:
% https://github.com/ZDTaylor/Deedy-Resume
%
% v1.4 author:
% Spencer Gass
%
% v1.4 repo:
% https://github.com/spencer-gass/resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Add various styling and section options and allow for multiple pages smoothly.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
%
% v1.3:
% 1. Removed MacFonts version as I have no desire to maintain it nor access to macOS
% 2. Switched column ordering
% 3. Changed font styles/colors for easier human readability
% 4. Added, removed, and rearranged sections to reflect my own experience
% 5. Hid last updated
%
% v1.2:
% 1. Added publications in place of societies.
% 2. Collapsed a portion of education.
% 3. Fixed a bug with alignment of overflowing long last updated dates on the top right.
%
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[10pt]{deedy-resume-reversed}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Spencer Gass}{ %\urlstyle{same}\href{http://example.com}{example.com}| \href{http://example2.co}{example2.co}\\
\href{mailto:spencer.gass@gmail.com}{spencer.gass@gmail.com} | \href{tel:12565413116}{256.541.3116} | \href{https://www.linkedin.com/in/spencer-gass/}{LinkedIn: spencer-gass} | \href{https://github.com/spencer-gass}{GitHub: spencer-gass}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{1.0\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{FPGA Digital Design Engineer}
\descript{| Kepler Communications | May 2024 – Present | Toronto, ON (Remote)}
%   IC3 May 2024 - Present
Current Responsibilities:
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Collaborating with network software, product hardware, and product management to integrate
the FPGA based MPLS router I designed into Kepler's satellites.
\item Subject matter expert on network hardware.
\end{tightemize}
Past Accomplishments:
\begin{tightemize}
\item Specified and designed an MPLS router with 100+Gbps throughput, and a high level of parametrization in SystemVerilog.
The design includes ingress, classification, forwarding, queuing, and egress subsystems.
Created a full automated test bench suite for verification.
\end{tightemize}
\sectionsep

\runsubsection{Senior FPGA Engineer}
\descript{| Adtran | June 2016 – April 2024 | Huntsville, AL (Remote 2020-2024)}
%   Untitled June 2016 - Oct 2019
%   II Oct 2019 - Oct 2020
%   Senior Oct 2020 - Jan 2024
%   Avanced Jan 2024 - present
Past Accomplishments:
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
%\item Contributed to the design specification for a telecom ASIC.
\item Created FPGA designs which implement key features for broadband access networking equipment and
supported those designs through their life cycle (design specification, RTL design, simulation,
synthesis/implementation, timing closure, on-target testing, and customer support).
\item Designs include: HSPON/XGS-PON/GPON DBA engines, 10G/100G Ethernet traffic generators/analyzers,
1G/10G/100G Ethernet MAC and SerDes, PCIe DMA, SyncE and board management.
%\item Collaborated with product management, engineers, and research staff to facilitate product development.
\item Lead the FPGA team's co-op program. Mentored and supervised 7 co-ops over a 2 year period.
%Co-ops start the semester with minimal RTL/FPGA knowledge and leave with a strong grasp of
%the fundamentals. By the end of the semester they are often able to contribute to a production FPGA design.
\item Inherited ownership of a 100 Gbps Ethernet traffic generator/analyzer and advanced it from minimum viable product to full function by refactoring RTL to close timing,
implementing technically difficult features like 100 Gbps packet capture, and DWRR scheduling, and implementing UI, application,
and driver features in Javascript, Python, and C. This is a ubiquitous internal product with over 250 units manufactured, saving the company 10s of millions of dollars.
%\item Contributed to the development of the 518F1 Adtran’s bestselling line card. Approximately  36,000 units sold, generating \$250M in revenue as of Q4 2023.
%Collaborated with a staff researcher to develop 25G Ethernet MAC and SerDes IP.
%Integrated and verified back plane Ethernet links.
\item Supported a principal engineer in the development of a multi-100G broadband Ethernet switch generating two awarded patents.
\item Resolved a critical customer issue shortly after inheriting ownership of the relevant IP which I was previously unfamiliar with.
Communicated progress to my VP and resolved the issue in time to salvage the relationship with the customer.
\item Recognized the limitations of the PCIe DMA engine used for FPGA register access and exception traffic,
and proactively created a higher performance, lower resource utilizing replacement. The new design is used in 14 FPGA designs on 8 product lines.
%\item Independently created and maintained 3 FPGA designs which perform SyncE, and board management functions on Adtran's SDX OLTs and aggregation switches.
%\item Inherited Ownership of Adtran’s Ethernet MAC and SerDes IP, used by nearly all FPGAs in Adtran’s product portfolio.
%Maintained existing IP and extended functionality.
%\item Created an FPGA based workaround for a rev A clock generator silicon bug which allowed us to ship hardware while waiting for rev B silicon.
%\item Collaborated with a cross functional team to develop a method for configuring large FPGAs to allow for faster boot times and more reliable FPGA initialization.
%\item Implemented a dynamic queue memory allocation system for Adtran’s Ethernet switch IP.
%This allows queues to increase in size in proportion to free memory before becoming full and discarding incoming packets,
%rather than assigning fixed memory sizes to queues.
\end{tightemize}
\sectionsep

\runsubsection{Engineering Co-op}
\descript{| Adtran | May 2013 – Dec 2014 | Huntsville, AL}
\begin{tightemize}
\item Worked for one semester each, three semester total, with DVT, hardware, and FPGA engineering groups.
\end{tightemize}
\sectionsep

%\runsubsection{Undergraduate Researcher}
%\descript{| CAVS | Aug 2015 – Dec 2015 | Starkville, MS}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\textbf{Georgia Institute of Technology} MS ECE | Aug 2019 | GPA: 3.4 / 4.0 \\
\textbf{Mississippi State University} BS EE | May 2016 | GPA: 3.8 / 4.0 \\
\sectionsep

\end{minipage}
\begin{minipage}[t]{1.0\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LEADERSHIP and MENTORSHIP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%\section{Leadership and Mentorship}
%%\vspace{\topsep} % Hacky fix for awkward extra vertical space
%%\begin{tightemize}
%%\item Led the FPGA group's co-op program since June 2022. Supervised/mentored 7 co-ops.
%%
%%\item Interviewed 26 co-ops/interns from 2016 to 2019.
%%\end{tightemize}
%%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\textbf{RTL Design:} VHDL | Verilog | System Verilog | Modelsim | Questasim | Vunit \\
\textbf{FPGA Design:} AMD | Xilinx | Vivado | Petalinux | Ultrascale+ | Versal | P4 \\
\textbf{Programming and Scripting:} Python | C++ | C | Javascript | Bash \\
\textbf{Relevant Technologies and Standards:} Ethernet | PCIe | AXI | DDR | HBM | TCP | MPLS \\
\textbf{Remote Collaboration:} Microsoft Teams | Git | GitHub | GitLab | Jira | Confluence \\
\textbf{Knowledge of:} UVM \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PATENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Patents}
\href{https://image-ppubs.uspto.gov/dirsearch-public/print/downloadPdf/11588821}{US 11,588,821 B1}
– Systems and Methods for Access Control List (ACL) Filtering – 2023-2-21 \\
\href{https://image-ppubs.uspto.gov/dirsearch-public/print/downloadPdf/12174748}{US 12,174,748 B1}
- Systems and Methods for Translating Memory Addresses – 2024-12-24 \\
\sectionsep

\end{minipage}

\end{document}  \documentclass[]{article}
